Changelog

### 2021-05-23 changelog.tex
Updates from Overleaf

\begin{enumerate}
\item \textbf{Fuzzing – need stronger motivation.}
\item \textbf{Discuss the limitations of your research
e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.}
\item \textbf{Can you extend your research (especially the quantification part) to include other side channel signals?}

@@

I have Incorporated some discussions into my dissertation. Please let me know if you have any feedback.

>>>>

\begin{enumerate}
\item \textbf{Fuzzing – Why did you use fuzzing?}

Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus may miss some-channel leakages. I have two choices at that time. First, I can use static analysis methods.

\item \textbf{Discuss the limitations of your research
e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.}
\item \textbf{Can you extend your research (especially the quantification part) to include other side channel signals?}

@@

I have incorporated some discussions into my dissertation. Please let me know if you have any feedback.
